# Distribution of Diseases burden by Countries

In this section, we studied the level of disease burden in countries where funded was received from NIAID. Our analysis focused on checking whether the level of disease burden correlate with countries' poverty level. In this study, we used the per capita GDP (obtained from the [world bank database](https://databank.worldbank.org/reports.aspx?source=2&series=NY.GDP.PCAP.PP.KD&country=#)) to evaluate countries' poverty level. Given the fact that, certain countries will have a higher population and therefore the burden may seems higher, we extracted the population size (again from the [world bank database](https://databank.worldbank.org/reports.aspx?source=2&series=NY.GDP.PCAP.PP.KD&country=#)) from 1990 to 2017 and took the average of both the population size and the per capita GDP of 1990 to 2017. The average population size was used to calculate the per capita burden in  a country (i.e. DALYs/population). 

All the data were scaled for ease of comparison and we plotted both all countries data and certain subset of the data that does not include countries in the northern or southern hemisphere since these are not in the tropical regions and should not have neglect tropical diseases. these plots were however included seprately in the presentation and thus not in this RMD file. 


```{r  message=FALSE, warning=FALSE, include=FALSE}

## Extract all country data
Burden.Countries <- All.Burden %>% 
  filter(location_id !="1") %>% # Remove Global and keep all countries
  filter(cause_id != "297", cause_id != "345",
         cause_id != "334", cause_id != "298",
         cause_id != "350") %>%  # remove TB, malaria, Influenza B, HIV/AIDS, and african tripano.
  select(c(cause_id,measure_id,measure_name,location_name,cause_name,year,val)) 


## Create associated diseases category
n3 <- dim(Burden.Countries)[1]

Associated.Disease3 <- rep(NA, n3) # Empty vector of size n3

for (i in 1:n3) {
if (Burden.Countries$cause_id[i] == "347") {
  Associated.Disease3[i] = "Leishmaniasis"
} else if (Burden.Countries$cause_id[i] == "346") {
  Associated.Disease3[i] = "Chagas"     
} else if (Burden.Countries$cause_id[i] == "351") {
  Associated.Disease3[i] = "Schistosomiasis"    
} else if (Burden.Countries$cause_id[i] == "357") {
  Associated.Disease3[i] = "Dengue"    
} else if (Burden.Countries$cause_id[i] == "354") {
  Associated.Disease3[i] = "Lymphatic Filariasis"
} else if (Burden.Countries$cause_id[i] == "353") {
  Associated.Disease3[i] = "Echinococcus"
} else if (Burden.Countries$cause_id[i] == "363") {
  Associated.Disease3[i] = "Hookworm"
} else if (Burden.Countries$cause_id[i] == "362") {
  Associated.Disease3[i] = "Trichuriasis"
} else {
  Associated.Disease3[i] = "Other"    
    }
}

## Add the disease category column
Burden.Countries$Diseases <- factor(Associated.Disease3,
                               levels = c("Chagas","Leishmaniasis","Schistosomiasis",
                                          "Lymphatic Filariasis", "Dengue", "Echinococcus",
                                      "Hookworm","Trichuriasis","Other"))



# Group by year and diseases
Burden.Countries2 <- Burden.Countries %>% 
  group_by(Diseases, measure_name, measure_id, location_name) %>% 
  summarize(Value = mean(val)) %>% 
  #distinct(Diseases, year, measure_name, location_name, .keep_all = TRUE) %>% 
  rename(Burden_id = "measure_id", Burden_name = "measure_name",
         Countries = "location_name") 

#View(head(Burden.Countries2,500))


######################### GDP PER CAPITA DATA
## Read in GDP Per Capita Data and country population size data
GDP <- read.xlsx("GDP_PerCapita_World_Development.xlsx", colNames = TRUE)
Pop <- read.xlsx("Population_World_Development.xlsx", colNames = TRUE)

#### calculate the mean of GDP and Population from 1990 to 2017 and remove all data except country name and mean value
## GDP
Mean_GDP <- GDP %>% 
  select(-c(Series.Name,Series.Code,Country.Code)) %>% 
  mutate(mean_gdp = select(.,-matches("Country.Name")) %>% 
  rowMeans(.)) %>% 
  select(-c("1990":"2017"))

colnames(Mean_GDP)[1] <- "Countries"
Mean_GDP$Countries <- levels(factor(Burden.Countries2$Countries)) # make sure the name are written the same way

## Population
Mean_Pop <- Pop %>% 
  select(-c(Series.Name,Series.Code,Country.Code)) %>% 
  mutate(mean_pop = select(.,-matches("Country.Name")) %>% 
  rowMeans(.)) %>% 
  select(-c("1990":"2017"))

colnames(Mean_Pop)[1] <- "Countries"
Mean_Pop$Countries <- levels(factor(Burden.Countries2$Countries)) # make sure the name are written the same way
#################################

## Merge GDP and Population data
GDP_Pop <- merge(Mean_GDP, Mean_Pop, by = "Countries")

## Merge the GDP, Pop, and Disease Burden dataset
Diseases_GDP <- merge(Burden.Countries2, GDP_Pop, by = "Countries")

## Remove the column "year" since we took average over year and it became irrelevant
Diseases_GDP <- Diseases_GDP %>% 
  mutate(GDP_rank = dense_rank(mean_gdp)) %>%
  mutate(Legend = paste(paste(Countries,round(mean_gdp), sep = " - $"),
         GDP_rank, sep = " - ")) 


```


## Disability-Adjusted Life Years (DALYs)


```{r  echo=FALSE, warning=FALSE, message=FALSE, fig.height=8, fig.width= 8}

## Create a function to transform the data from long to wide table
long_to_wide <- function(Data, BurdenID, PerCapitaBurden){
  # Data is the merge GDP and Disease burden data
  # BurdenID is the Disease Burden ID ranging from 1 to 6 which must be input in quotation
  # PerCapitaBurden is either "Yes" to calculate Per Capita Disease Burden or other string for
  # scale normal burden data
  sub_data <- subset(Data, Burden_id == BurdenID)
  sub_data_long <- spread(sub_data,Diseases,Value) # use value instead of per.cap.burden to see actual burden value
  sub_data_long2 <- sub_data_long %>% arrange(GDP_rank) # order by GDP rank
  
  sub.sub_data_long <- sub_data_long2[,-c(1:7)] # remove irrelevant data
  
  # create an empty matrix of row = # of countries, column = # of diseases 
  sub.sub_data_long2 <- matrix(NA,nrow = dim(sub.sub_data_long)[1], dim(sub.sub_data_long)[2])
  
  ##Select Per capita or the disease burden itself
  
  if (PerCapitaBurden=="Yes"){
  # divide the burden by their corresponding population size
  for (i in 1:dim(sub.sub_data_long)[1]){
    sub.sub_data_long2[i,] <- as.numeric(sub.sub_data_long[i,])/sub_data_long$mean_pop[i]
  }
  } else {
  for (i in 1:dim(sub.sub_data_long)[1]){
     sub.sub_data_long2[i,] <- as.numeric(sub.sub_data_long[i,])/1
  }
  }
 
  rownames(sub.sub_data_long2) <- sub_data_long2$Legend
  colnames(sub.sub_data_long2) <- colnames(sub.sub_data_long)
  #return(as.matrix(sub.sub_data_long2))
  return(scale(sub.sub_data_long2, center = FALSE, scale = TRUE))
}



##################### PLOTTING
## low, mid, high: Colors to use for the Lowest, middle, and highest values. 
## We used blue, white, and red for our value
  # the resulting matrix is scaled columnwise



# heatmap.2(DALYs, scale = "none", col = bluered(20), 
#           trace = "none", density.info = "none", keysize = 0.8, margins = c(15,15), cexRow = 1.3, cexCol = 1.3,
#           sepcolor = "black", sepwidth=c(0.1,0.1))


         
## DALYs
DALYs <- long_to_wide(Diseases_GDP,"2", "Yes")
pheatmap(DALYs, scale = "none", legend = TRUE,cluster_rows = FALSE, fontsize = 13)

```

## Years of Life Lost (YLLs)

```{r  echo=FALSE, warning=FALSE, message=FALSE, fig.height=8, fig.width= 8}
## YLLs (Years of Life Lost)
YLLs <- long_to_wide(Diseases_GDP,"4","Yes")
pheatmap(YLLs, scale = "none", legend = TRUE, cluster_rows = FALSE, fontsize = 13)
```

## Years Lived with Disability (YLDs)

```{r  echo=FALSE, warning=FALSE, message=FALSE, fig.height=8, fig.width= 8}
## YLDs (Years Lived with Disability)
YLDs <- long_to_wide(Diseases_GDP,"3","Yes")
pheatmap(YLDs, scale = "none", legend = TRUE, cluster_rows = FALSE, fontsize = 13)

```

## Mortality

```{r  echo=FALSE, warning=FALSE, message=FALSE, fig.height=8, fig.width= 8}
## Deaths
Deaths <- long_to_wide(Diseases_GDP,"1","Yes")
pheatmap(Deaths, scale = "none", legend = TRUE,cluster_rows = FALSE, fontsize = 13)
```

## Incidence

```{r  echo=FALSE, warning=FALSE, message=FALSE, fig.height=8, fig.width= 8}
## Incidence
Incidence <- long_to_wide(Diseases_GDP,"6","Yes")
pheatmap(Incidence[,c(1,2,5,6,9)], scale = "none", legend = TRUE,cluster_rows = FALSE,
         fontsize = 13)
```

## Prevalence

```{r  echo=FALSE, warning=FALSE, message=FALSE, fig.height=8, fig.width= 8}
## Prevalence
Prevalence <- long_to_wide(Diseases_GDP,"5","Yes")
pheatmap(Prevalence[,c(1,2,5,6,9)], scale = "none", legend = TRUE, cluster_rows = FALSE,
         fontsize = 13)

```


The level of burden in countries change depending on disease burden metric used. However, Brazil Phillipines and Nicaragua saw a very high level of disease burden. Leishmaniasis, Chagas, and Schistosomiasis were the most concentrated disease in Brazil while Dengue, Lymphatic Filariasis, and Trichuriasis were the most concentrated in the other countries. Asd should be expected, countries with the highest GDP per capita did not see any increase a high level of disease burden given the fact that they were not in a tropical area. 



